`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
completed table8

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $L$ & number of field basis functions  \\
    	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
    	$\mathbf{x}_t$ & state vector at time $t$ \\
    	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
    	$\theta$ & vector of connectivity kernel parameters \\
    	$\Gamma$ & inner product of field basis functions \\
    	$q()$ & state function \\
    	$k()$ & maps into to discrete state of input function \\
    	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\
    	$\mathbf{C}$ & observation matrix \\
    \end{tabular}
    \caption{Decomposition}
\end{table}

>>>>

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $L$ & number of field basis functions  \\
    	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
    	$\mathbf{x}_t$ & state vector at time $t$ \\
    	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
    	$\theta$ & vector of connectivity kernel parameters \\
    	$\Gamma$ & inner product of field basis functions \\
    	$q()$ & state function \\
    	$Q()$ & state function \\
	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
    	$\mathbf{e}_t$ & state disturbance \\
	$\Sigma_e$ &state disturbance covariance matrix\\
	$\mathbf{\epsilon}_t$ & observation noise \\
	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
    	$\mathbf{C}$ & observation matrix \\
	$c_{ij}$& elements of observation matrix
    \end{tabular}
    \caption{Decomposition}
\end{table}
